---
title: "Auto Losses and Bikeshare Analysis - Shahin Shakeri"
output:
  pdf_document: default
  html_notebook: default
---

I use R notebooks in RStudio cloud and the data is stored in the clound on my google drive. I submitted this notebook in original format which can be simply be opened in R desktop and run.

# 1- Auto Losses

## 1.a) Two door cars are correlated with more losses
```{r}
library('lattice')
Autoloss <- read.csv(url("https://drive.google.com/uc?export=download&id=1cbk_KGdo5sfY0c4_ALB5ULTeYQ87uU6k"),na.strings = '?')
Autoloss <-na.omit (Autoloss)
ByDoors=tapply(Autoloss$Losses, Autoloss$NumDoors, mean)
barplot(ByDoors, col = rainbow(15),xlab="Number of Doors",ylab = "Loss",ylim=c(0,150))

```

## 1.b) Sedans have the lowest losses among the least costly losses. This doesn’t mean the entire dataset follows this pattern.
```{r}
Lowest<- Autoloss[order(Autoloss$Losses,decreasing=FALSE),][1:10,]
Lowest<-tapply(Lowest$Losses,Lowest$BodyStyle , mean)
Lowest

```

## 1.c) Sedans and Hatchbacks have the widest spread of losses. The losses in sedan are skewed towards the lower end where in the other styles are more or less evenly distributed.
```{r}
ByWheels<-tapply(Autoloss$Losses,Autoloss$BodyStyle,mean)
ByWheels
boxplot(Losses~BodyStyle,data=Autoloss ,col = rainbow(15))

```

## 1.d) Lower priced car have costlier loses than higher priced cars on average 
```{r}
xyplot(Losses~Price,data=Autoloss, col = rainbow(50))
```

# 2 -Bikeshare
## 2.a) We run a simple regression for Rentals~Temperature
```{r}
Bikeshare <- read.csv(url("https://drive.google.com/uc?export=download&id=1jtfh-qmyDM3l_nU3AkPP_ZsepL-jHW8I"),na.strings = '?')
LModel=lm(Rentals~Temperature,data=Bikeshare)
{plot(Bikeshare$Temperature,Bikeshare$Rentals,col='blue') 
abline(LModel,col="red" )}
```

```{r}
summary(LModel)
```
## For every 1 change to normalized Temperature, Rentals change by 6640.7. Accoring to small p <.05 this is significant

## 2.b) We run a simple regression for Rentals~Humidity
```{r}
LModel=lm(Rentals~Humidity,data=Bikeshare)
{plot(Bikeshare$Humidity,Bikeshare$Rentals,col='blue') 
abline(LModel,col="red" )}
```

```{r}
summary(LModel)
```
## For every 1 increase to normalized Humidity, Rentals change by -1369.1 . Accoring to small p <.05 this is significant but the R-squared:  0.01013 shows this is not a good model

## 2.c) We run a simple regression for Rentals~Windspeed
```{r}
LModel=lm(Rentals~Windspeed,data=Bikeshare)
{plot(Bikeshare$Windspeed,Bikeshare$Rentals,col='blue') 
abline(LModel,col="red" )}
```

```{r}
summary(LModel)
```
## For every 1 increase to normalized Windspeed, Rentals change by -5862.9. Accoring to small p <.05 this is significant but R-squared:  0.05501 shows this is not significant
