---
title: '#4 Auto Loss Analysis - Shahin Shakeri'
output:
  pdf_document: default
  word_document: default
  html_notebook: default
---


# 1- Autoloss
## a) Using forward stepwise method:
```{r}
Autoloss <- read.csv(url("https://drive.google.com/uc?export=download&id=1-QuNWq7k4w3c8kBJ8BedIK1m-cpwORiV"),na.strings = '?')
Autoloss <-na.omit (Autoloss)

library(leaps)
regfit.fwd=regsubsets(Losses~., data = Autoloss,nvmax=15, method="forward")
summary=summary(regfit.fwd)
preds=summary$which[10,][-1]
names(preds)[preds==TRUE]

```
### The best model with 10 predictors has the above columns.
## b) What number of predictors minimizes Cp?
```{r}
min=which.min(summary$cp)
min
preds=summary$which[min,][-1]
names(preds)[preds==TRUE]

```
### The best model which minimizes Cp has the above 5 predictors


# 2- Autoloss
## a) LASSO model with 5-fold cross validation
```{r}
library(glmnet)
set.seed(1)
x=model.matrix(Losses~.,data=Autoloss)[,-1]
y=Autoloss$Losses
cv.out=cv.glmnet(x,y,alpha=1,nfolds=5)
bestLam=cv.out$lambda.min
bestLam
```

## b) LASSO with best lamda
```{r}
cv.out=glmnet(x,y,alpha=1,lambda =  bestLam )
coefs=coef(cv.out)
coefs
```
### Predictors that are not zero are in the model with best lambda.

# 3 Answers for a dataset with P predictors

### i True
### ii True
### iii True
### iv True
### v True
